%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Education}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------
\cventry
{PhD in Medical Biophysics (Proteogenomics)} % Degree
{University Of Toronto} % Institution
{Toronto, ON,  Canada} % Location
	{2012 - 2017 (October)} % Date(s)
{ % Description(s) bullet points
 \begin{cvitems}
 \item {To inform decision makers on key issues in a multi-disciplinary setting, outlined key problems and ranked solutions delivered by succinct 2-line written communications and maximally 15-minute presentations; key decision makers were informed on issues arising in the project and timely achieved project milestones.}
 \item {To deliver computational expertise to a cancer biomarker discovery lab specialized in clinical proteomics, acquired mass spectrometry techniques and data analysis mastery, developed a novel analytical pipeline that that identifies cancer-causing mutations; customer has adopted use of the pipeline in analyzing all clinical samples.}
 \item {\textbf{Business:} Finalist in a pitch competition for \$50,000 in startup funding, participant in 2 case study competitions.}
 \item {\textbf{Skills:} Project management, pipeline development, critical thinking, data analysis, oral and written communication}
 \item {\textbf{Languages:} Perl, R, PostgreSQL}
 \end{cvitems}
}

\cventry
{Masters in Biochemistry (Bioinformatics)} % Degree
{Dalhousie University} % Institution
{Halifax, NS, Canada} % Location
{September 2009 - 2012} % Date(s)
{
 \begin{cvitems}
 \item {Understanding the contraints imposed by protein structure on protein evolution is of critical importance to protein engineering. Working closely with a statistician and a biologist, I developed and implemented a mathematical model of protein evolution that integrated protein structure. My model significantly out-performed standard models that neglect protein structure.}
 \item {\textbf{Skills:} Math/Stats, algorithm development, pipeline development, data analysis, writing and presentation}
 \item {\textbf{Languages:} Python, R, C/C++}
 \end{cvitems}
}

\cventry
{Double Major Biochemistry (Honours,) and Computer Science} % Degree
{University of Victoria} % Institution
{Victoria, BC, Canada} % Location
{2003 - 2008} % Date(s)
{
\begin{cvitems}
 \item {The ABO blood group enzyme plays a critical role in graft vs host disease and understanding how this enzyme recognizes its substrate was badly needed. I analyzed the diffraction data obtained     from eighty crystallography experiments. Results supported an international collaborative research effort that clarified important behavioral intricacies of the ABO blood group enzymes.}
 \item {Excellent understanding of biochemistry, from  genomics to proteomics. Computer Science degree supports adaptive quantitative biology.}
 \item {\textbf{Languages:} Java, R, C, Python}
\end{cvitems}
}
%\cventry
%{Double Major Biochemistry (Honours,) & Computer Science} % Degree
%{University of Victoria} % Institution
%{Victoria, British Columbia, Canada} % Location
%{2003 - 2008} % Date(s)
%{
%\begin{cvitems}
%\item {Biochemistry}
%\item {Biochemistry provides an understanding of the theory, the experimental methods and, the limits of those methods when used to probe questions in genomics and proteomics. Computer Science provides the tools with which to mine data and visualize results effectively.}
%\end{cvitems}
%}
%------------------------------------------------
\end{cventries}
