%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}
%------------------------------------------------

\cventry
{Data Scientist} % Job title
{Department of Computer Science, University of Victoria} % Organization
{Victoria, BC Canada} % Location
{2008-2008} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {To gain insights into glycosyltransferase enzyme family mechanisms. I employed a machine learning approach to intelligently distinguish between two classes of enzymes with unknown mechanism from crystal structures.}
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Biochemist and Data Analyst} % Job title
{Dept. Biochemistry, University of Victoria} % Organization
{Victoria, BC, Canada} % Location
{2005-2009} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {To develop strategies for Sample preparation of As a technician and student, I purified proteins for crystallization and analyzed the results of x-ray crystallography experiments.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Home Care Aide} % Job title
{Cridge Brain injury Centre} % Organization
{Victoria, BC, Canada} % Location
{2007-2008} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Assisted ten head injured patients at a residence home with their personal needs. Ensured their timely medication and overall wellness. Improved, overall resident lifestyle by engaging in after-work social activities.}
\item {To help a visually impaired resident connect with family, developed a program in Python that read contact information aloud and dialed the number of the selected contact; resident used the program frequently resulting in reduced feelings of isolation and greater social independence}
\end{cvitems} 
}

%------------------------------------------------

%\cventry
%{Research Assistant} % Job title
%{Forestry Genome BC} % Organization
%{Vancouver, BC, Canada} % Location
%{2004-2004} % Date(s)
%{ % Description(s) of tasks/responsibilities
%\begin{cvitems}
%\item {Performed QA/QC analysis on a set of plasmids used in the sequencing of the spruce genome}
%\end{cvitems}
%}

%------------------------------------------------

\cventry
{Forest ecology researcher} % Job title
{Pacific Forestry Center} % Organization
{Victoria, BC, Canada} % Location
{2003-2003} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Understanding and modelling insect infestations plays an important role in predicting outbreaks. Worked in a two man team for four months in a remote region of British Columbia collecting data on an insect infestation. Careful planning, dedication and long hours ensured that a very high quality dataset was collected.}
\end{cvitems}
}
%------------------------------------------------
\end{cventries}
