%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Publications}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}
	\cventryshort                                                                                                                                                                                                    
	%{} % Degree
	%{} % Institution
	%{} % Location
	%{} % Date(s)
	{
	\begin{cvenum}
	\item \textbf{Alfaro JA}, Ignatchenko A, Ignachenko V, Sinha A, Boutros C and Kislinger T. Detecting protein variants by mass-spectrometry: A comprehensive study in cancer cell-lines. (Submitted) Genome Medicine. 
	\item Sinha A, \textbf{Alfaro JA}, and Kislinger T. 2017. Characterization of Protein Content Present in Exosomes Isolated from Conditioned Media and Urine. Current Protocols in Protein Science, 24-9.
	\item \textbf{Alfaro JA}, Sinha A, Kislinger T, Boutros PC. Onco-proteogenomics: cancer proteomics joins forces with genomics.  2014. Nat Methods. 11(11):1107-13.
	\item Weinreb I, Piscuoglio S, Martelotto LG, Waggott D, Ng CK, Perez-Ordonez B, Harding NJ, \textbf{Alfaro JA}, \textit{et al.} Hotspot activating PRKD1 somatic mutations in polymorphous low-grade adenocarcinomas of the salivary glands. 2014. Nat Genet. 46(11):1166-9.
	\item Planello AC, Ji J, Sharma V, Singhania R, Mbabaali F, Müller F, \textbf{Alfaro JA}, Bock C, De Carvalho DD, Batada NN.  Aberrant DNA methylation reprogramming during induced pluripotent stem cell generation is dependent on the choice of reprogramming factors. 2014. Cell Regen. 3(1). 1.
	\item Johal AR, Blackler RJ, \textbf{Alfaro JA}, Schuman B, Borisova S, Evans SV. Glycobiology. pH-induced conformational changes in human ABO(H) blood group glycosyltransferases confirm the importance of electrostatic interactions in the formation of the semi-closed state. 2014. 24(3):237-46.
	\item Johal AR, Schuman B, \textbf{Alfaro JA}, Borisova S, Seto NOL and Evans SV. Sequence-dependent effects of cryoprotectants on the active sites of the human ABO(H) blood group A and B glycosyltransferases. 2012. Acta Cryst. D68, 268–276.
	\item \textbf{Alfaro JA}, Zheng RB, Persson M, Letts JA, Polakowski R, Bai Y, Borisova SN, Seto NO, Lowary TL, Palcic MM, Evans SV. ABO(H) Blood Group A and B Glycosyltransferases Recognize Substrate via Specific Conformational Changes. 2008.  J Biol Chem. 283(15):10097-10108.
    \end{cvenum}
    }
\end{cventries}
